Hot and fresh: Pervasive climate stressors of seagrass in a large Gulf coast estuary

### 2023-09-15 manu-draft.qmd
more models of change over time

>>>>

### Models

All models excluded Lower Tampa Bay because of minimal seagrass change over time. Also attempted to evaluate total and change as binary.

GLMs of percent change each year by Sal, Temp, with year and bay segment interactions.  Attempted different windows of time from approximate seagrass sample date, 30 days to one year. The best model was one that included an effect of Salinity and an interaction with bay segment.  Hillsborough Bay showed a strong response of increasing likelihood of seagrass loss with number of days when salinity was below the threshold.

Then GAMs were evaluated looking at total by Salinity, with interaction of year and bay segment.  Also created a model looking at percent change vs Temp and year/bay segment interaction.

Show plots of both the glm and gams.
